### 2021-04-26 input/abstract.tex
address most of comments, but NOT related work + spacing appeared between II and III

  %%% Our proposal
  \noindent In this paper, we abstract content indexing as distributed
  partitioning:
  every \process only indexes its closest replica, and
  connected \processes with similar index compose a partition. Our
  decentralized implementation \NAME
  \begin{inparaenum}[(i)]
  \item is efficient, for it uses partitions to lock down the traffic
    generated by its operations to relevant \processes, yet it
  \item guarantees that every \process eventually acknowledges its
    partition despite concurrent operations.
  \end{inparaenum}
  %% When a \node replicates a content, it notifies all \nodes (new
  %% members of its partition) that are closer from it than any other
  %% replica; When a \node destroys a replica, it notifies members of
  %% its partition to switch to another closer partition. \NAME
  %% guarantees that eventually, every \process knows its best
  %% partition, hence its closest replica, despite concurrent
  %% operations and receipt orders.
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and termination time. As
  such, \NAME can constitute the building block of new geo-distributed
  services.
\end{abstract}

\begin{IEEEkeywords}
Edge infrastructures, decentralized content indexing, scoped
broadcast, logical partitioning protocol
\end{IEEEkeywords}

>>>>

  %%% Our proposal
  \noindent In this paper, we abstract content indexing as distributed
  partitioning:
  every \process only indexes its closest replica, and
  connected \processes with a similar index compose a partition. Our
  decentralized implementation \NAME is
  \begin{inparaenum}[(i)]
  \item efficient, for it uses partitions to lock down the traffic
    generated by its operations to relevant \processes, yet it
  \item guarantees that every \process eventually acknowledges its
    partition despite concurrent operations.
  \end{inparaenum}
  %% When a \node replicates a content, it notifies all \nodes (new
  %% members of its partition) that are closer from it than any other
  %% replica; When a \node destroys a replica, it notifies members of
  %% its partition to switch to another closer partition. \NAME
  %% guarantees that eventually, every \process knows its best
  %% partition, hence its closest replica, despite concurrent
  %% operations and receipt orders.
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and termination time. As
  such, \NAME can constitute a new building block for geo-distributed
  services.
\end{abstract}

%% \begin{IEEEkeywords}
%% Edge infrastructures, decentralized content indexing, scoped
%% broadcast, logical partitioning protocol
%% \end{IEEEkeywords}

### 2021-04-26 input/background.tex
reworkd conclusion
address most of comments, but NOT related work + spacing appeared between II and III

Numerous studies addressed content indexing in geo-distributed
infrastructures ranging from centralized services to fully
decentralized approaches~\cite{squirrel}. We advocate for the latter where
\processes host the service themselves so they do not need to request
remote -- possibly far away third-party -- entities to retrieve their
content location.  In this paper, we tackle the content indexing issue
as a dynamic logical partitioning problem. This section motivates this
shift and explains the shortcomings of existing implementations.

@@

Then, in Figure~\ref{fig:partition_intuitionB}, another \Process~$G$
creates a replica of this content. Similarly to \Process~$R$, it
notifies other \processes of this new replica. However, to avoid that
north \processes request its replica, and south \processes request the
northern replica, \processes hosting a replica must add \emph{location
information} along with their notifications. As consequence, every
\process eventually knows every replica location and can download from
its closest host. \underline{R}ed \processes would request
\Process~$R$ while \underline{g}reen \processes would request
\Process~$G$.

@@

Then, in Figure~\ref{fig:partition_intuitionC}, another \Process~$B$
creates a replica of this content. Similarly to \Process~$R$ and
\Process~$G$, \Process~$B$ can notify other \processes of this new
replica. However, the set of \processes that could actually use this
new replica is actually much smaller than the network size. Uniform
reliable broadcast is not designed for such context and would generate
a lot of unnecessary traffic. Instead, \processes need a communication
primitive that propagates notifications within a scope by evaluating a
predicate, starting at its broadcaster (the \emph{source}).  In other
terms, \processes propagate notifications as long as they consider
them useful based on location information they carry. We call such
primitive \emph{scoped broadcast}, for messages transitively reach a
subset of interconnected \processes (the \emph{scope}). Using this
primitive, \processes can lock down the traffic of content indexing to
relevant \processes.

@@

Every \process ends up with at least one known replica that is its
closest. The set of interconnected \processes with the same closest
replica is a \emph{partition}. Every \process belongs to one, and only
one, partition. Contrarily to membership protocols that choose
neighboring \processes to communicate with based on metrics~\cite{t-man},
\processes in our context have no control over their neighboring
\processes: they cannot add nor remove communication links.

@@

Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
destroys its replica. Every \processes that belonged to its green
partition must choose another partition to be in. While it makes sense
for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
once again scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
\processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partitions would block the
propagation of other partitions.
\end{asparadesc}

Next Section details the properties of adaptive scoped broadcast in
dynamic networks, and provides an implementation called \NAME along with its
complexity.

>>>>

Numerous studies addressed content indexing in geo-distributed
infrastructures ranging from centralized services to fully
decentralized approaches~\cite{squirrel}. We advocate for the latter
where \processes host the service themselves so they do not need to
request remote -- possibly far away third-party -- entities to
retrieve their content location.  In this paper, we tackle the content
indexing issue as a dynamic logical partitioning problem. This section
motivates our positioning and explains the shortcomings of existing
implementations.

@@

Then, in Figure~\ref{fig:partition_intuitionB}, another \Process~$G$
creates a replica of this content. Similarly to \Process~$R$, it
notifies other \processes of this new replica. However, to avoid that
north \processes request its replica, and south \processes request the
northern one, \processes hosting a replica must add \emph{location
information} along with their notifications. As consequence, every
\process eventually knows every replica location and can download from
its closest host. \underline{R}ed \processes would request
\Process~$R$ while \underline{g}reen \processes would request
\Process~$G$.

@@

Then, in Figure~\ref{fig:partition_intuitionC}, another \Process~$B$
creates a replica of this content. Similarly to \Process~$R$ and
\Process~$G$, \Process~$B$ can notify other \processes of this new
replica. However, the set of \processes that could actually use this
new replica is actually much smaller than the network size. Uniform
reliable broadcast is not designed for such a context and would
generate a lot of unnecessary traffic. Instead, \processes need a
communication primitive that propagates notifications within a scope
by evaluating a predicate, starting at its broadcaster (the
\emph{source}).  In other terms, \processes propagate notifications as
long as they consider them useful based on location information they
carry. We call such primitive \emph{scoped broadcast} (see
Section~\ref{subsec:scoped}), for messages transitively reach a subset
of interconnected \processes (the \emph{scope}). Using this primitive,
\processes can lock down the traffic of content indexing to relevant
\processes.

@@

Every \process ends up with at least one known replica that is its
closest. The set of interconnected \processes with the same closest
replica is a \emph{partition}. Every \process belongs to one, and only
one, partition (see Section~\ref{subsec:consistent}).

%% Contrarily to membership
%% protocols that choose neighboring \processes to communicate with based
%% on metrics~\cite{t-man}, \processes in our context have no control
%% over their neighboring \processes: they cannot add nor remove
%% communication links.

@@

Finally, in Figure~\ref{fig:partition_intuitionD}, \Process~$G$
destroys its replica. Every \processes that belonged to its green
partition must choose another partition to be in. While it makes sense
for \Process~$G$ to scoped broadcast its removal, \Process~$B$ and
\Process~$R$ cannot afford to continuously advertise their replica to
fill the gap left open by \Process~$G$. Instead, we want to trigger
once again scoped broadcast at bordering \processes of red and blue
partitions. The scope of scoped broadcast changes over receipts by
\processes. Dynamic partitioning raises additional challenges related
to concurrent operations where removed partitions would block the
propagation of other partitions (see Section~\ref{subsec:dynamic}).
\end{asparadesc}

Next Section details the properties of scoped broadcast and dynamic
partitioning in dynamic networks, and provides an implementation
called \NAME along with its complexity.

\vfill
\TODO{spacing.}
\newpage

### 2021-04-26 input/conclusion.tex
wip
address most of comments, but NOT related work + spacing appeared between II and III

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised in order to mitigate as
much as possible traffic between \processes.  In this paper, we
tackled the problem of content indexing, a key service for storage
systems.
%
We proposed to address this problem as a dynamic logical partitioning
in dynamic networks where partitions grow and shrink to reflect
content and replicas locations, as well as infrastructure
changes. Using an efficient communication primitive called scoped
broadcast, each \process composing the infrastructure eventually knows
the \process hosting the best replica of specific content.  The
challenge resides in handling concurrent operations that may impair
the propagation of messages, and in turns, lead to inconsistent
partitioning. 
%% The major difficulty lies in concurrent operations, each having a
%% different scope, and ensure the correct convergence of the system.  We
%% defined, in particular, multiple properties that highlight this
%% complexity.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME.  Our simulations confirmed that
\processes quickly reach consistent partitioning together, and that
the generated traffic remains locked down to partitions.
%% correctness of our protocol as well as the confinement of
%% the traffic only where it is needed.

>>>>

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised in order to mitigate as
much as possible traffic between \processes.  In this paper, we
tackled the problem of content indexing, a key service for storage
systems.
%
We proposed to address this problem as a dynamic logical partitioning
where partitions grow and shrink to reflect content and replicas
locations, as well as infrastructure changes. Using an efficient
communication primitive called scoped broadcast, each \process
composing the infrastructure eventually knows the \process hosting the
best replica of specific content.  The challenge resides in handling
concurrent operations that may impair the propagation of messages, and
in turns, lead to inconsistent partitioning.
%% The major difficulty lies in concurrent operations, each having a
%% different scope, and ensure the correct convergence of the system.  We
%% defined, in particular, multiple properties that highlight this
%% complexity.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME.  Our simulations confirmed that
\processes quickly reach consistent partitioning together, and that
the generated traffic remains locked down to partitions.
%% correctness of our protocol as well as the confinement of
%% the traffic only where it is needed.

### 2021-04-26 input/experiments.tex
address most of comments, but NOT related work + spacing appeared between II and III

\noindent We evaluate dynamic scoped broadcast. First, we create 100
partitions one at a time: \processes reach consistent partitioning
before we create each new partition. Second, we remove every partition
one at a time, in the order of their creation, hence starting from the
first and oldest partition that had been added.

@@

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are more expensive than add operations. Indeed, the
top part of the figure shows that after 21 seconds, when the
experiment involves removals, traffic includes both $\alpha$'s and
$\delta$'s. The latter aims at removing stale information and
triggering competition while the former aims at updating shortest
paths. As corollary, the convergence time increases, for $\delta$
messages must reach every partition border before any sound
competitors propagate their partition. It is worth noting that this
delete operation involves concurrency: removals continue to propagate
while the competition is already partially triggered and propagating.

@@

\noindent We evaluate the traffic of \NAME by measuring the average
number of messages per \process over the experiments. In the first
experiment, at $50$~ms, only one \process becomes source, hence there
is only one partition for the whole distributed system. In the second
experiment, at $50$~ms, two \processes become sources, one per
cluster. Afterwards both scenarios are identical. At $850$~ms, we
remove the link between the two clusters. At $1.7$~s, we insert this
link again.

@@

\noindent Figure~\ref{fig:geant} shows that, when adding the
inter-continental link again, the two clusters can communicate
again. In the experiment involving one source for two clusters, it
generates traffic. After a $200$ ms delay corresponding to
the new link latency, the cut off cluster starts to communicate
$\alpha$ messages again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source located in their
respective cluster.

\noindent Overall, this experimentation empirically demonstrates the
benefits of \NAME in the context of geo-distributed infrastructures,
e.g., inter-connected autonomous systems where \processes may join or
leave or crash, communications links may be added or removed. \NAME
coupled with replication strategies designed for the Edge would allow
locking down the traffic of replica indexing, while providing every
\process with quick access to replicated content.

@@

Next Section reviews state-of-the-art approaches for content indexing
in geo-distributed infrastructures and explains their shortcomings in
such context.

>>>>

\noindent We evaluate dynamic consistent partitioning. First, we
create 100 partitions one at a time: \processes reach consistent
partitioning before we create each new partition. Second, we remove
every partition one at a time, in the order of their creation, hence
starting from the first and oldest partition that had been added.

@@

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are more expensive than add operations. Indeed, the
top part of the figure shows that after 21 seconds, when the
experiment involves removals, traffic includes both $\alpha$'s and
$\delta$'s. The latter aims at removing stale information and
triggering competition while the former aims at updating shortest
paths. As corollary, the convergence time increases, for $\delta$
messages must reach the partition borders before sound competitors
propagate their partition. It is worth noting that this delete
operation involves concurrency: removals continue to propagate while
the competition is already partially triggered and propagating.

@@

\noindent We evaluate the traffic of \NAME by measuring the average
number of messages per \process over the experiments. In the first
experiment, at $50$~ms, only one \process becomes source, hence there
is only one partition for the whole distributed system. In the second
experiment, at $50$~ms, two \processes become sources, one per
cluster. Afterwards both scenarios are identical. At $850$~ms, we
remove the link between the two clusters. At $1.7$~s, we insert back this
link.

@@

\noindent Figure~\ref{fig:geant} shows that, when adding back the
inter-continental link, the two clusters can communicate again. In the
experiment involving one source for two clusters, it generates
traffic. After a $200$ ms delay corresponding to the link latency, the
cut off cluster starts to communicate $\alpha$ messages
again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source located in their
respective cluster.

\noindent Overall, this experimentation empirically demonstrates the
benefits of \NAME in the context of geo-distributed infrastructures,
e.g., inter-connected autonomous systems where \processes and
communications links may be added and removed at any time. \NAME
coupled with replication strategies designed for Edge infrastructures
would allow locking down the traffic of replica indexing, while
providing every \process with quick access to replicated content.

@@

Next Section reviews state-of-the-art approaches for content indexing
in geo-distributed infrastructures and explains their shortcomings.

### 2021-04-26 input/introduction.tex
address most of comments, but NOT related work + spacing appeared between II and III

In recent years, the data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This shift aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier, foggy_cache, shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,
  confais2017performance, fogstore, hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud, rely on distributed hash tables~\cite{maymounkov2002kademlia}
spread across the different \processes composing the
infrastructure. When a client wants to access specific content, it
requests a remote \process to provide at least one \process identity
to retrieve this content from. After it retrieved the content, the
client can create another replica to improve the performance of future
accesses, but it must contact the content indexing service again to
notify of such change.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

These approaches directly contradict with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays~\cite{asrese2019measuring, doan2019tracing} that
occur even before the actual download started.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple replica hosts,
yet only keeping the fastest answer. In turns, clients either waste
network resources, or face lower response time.
%% there is no information to select the ``best'' node among the
%% possible candidates from which the content could be retrieved. In
%% most cases, this results in parallel requests performed by the
%% client node to each candidate with the goal of retrieving the
%% content as efficient as possible.

@@

Instead, a \process creating a replica should notify all and only
\processes that have no closer replica in the system. This would
create interconnected sets of \processes, or \emph{partitions},
gathered around a \emph{source} being their respective replica. A
\process deleting its replica should notify all members of its
partition so they can rally their current closest partition. A
periodic advertisement protocol already provides both these operations
for routing purposes~\cite{hemmati2015namebased}. However, its
functioning requires
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item to finely tune physical-time-based intervals that depend on
  network topology parameters such as network diameter.
\end{inparaenum}

>>>>

In recent years, the data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This change aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier, foggy_cache, shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,
  confais2017performance, fogstore, hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud, rely on \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{maymounkov2002kademlia} spread across
the different \processes composing the infrastructure. When a client
wants to access specific content, it requests a remote \process to
provide at least one \process identity to retrieve this content
from. After it retrieved the content, the client can create another
replica to improve the performance of future accesses, but it must
contact the content indexing service again to notify of such a change.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

These approaches contradict with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays~\cite{asrese2019measuring, doan2019tracing} that
occur even before the actual download started.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple replica hosts,
yet only keeping the fastest answer. In turns, clients either waste
network resources, or face lower response time.
%% there is no information to select the ``best'' node among the
%% possible candidates from which the content could be retrieved. In
%% most cases, this results in parallel requests performed by the
%% client node to each candidate with the goal of retrieving the
%% content as efficient as possible.

@@

Instead, a \process creating a replica should notify all and only
\processes that have no closer replica in the system. This would
create interconnected sets of \processes, or \emph{partitions},
gathered around a \emph{source} being their respective replica. A
\process deleting its replica should notify all members of its
partition so they can identify and rally their new closest
partition. A periodic advertisement protocol already provides both
operations for routing purposes~\cite{hemmati2015namebased}. However,
its functioning requires
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item to finely tune physical-time-based intervals that depend on
  network topology parameters such as network diameter.
\end{inparaenum}
